---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bojackpalette

<!-- badges: start -->
<!-- badges: end -->

The goal of bojackpalette is to provide clean and coordinated color palettes inspired by characters and scenes from Bojack Horseman.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mwhalen18/bojackpalette")
```
## Example

There are currently `r length(bojackpalette::bojack_palettes)` total palettes to choose from. 

```{r example}
library(bojackpalette)

names(bojack_palettes)
```

You can create a palette using the following command:

```{r}
palette = bojack_palette("Bojack")
```

You can also specify a specific number of colors from the palette.

```{r, out.width="300px", results="show"}
bojack_palette("SarahLynn", 5)
```

## Palettes

```{r, echo = FALSE, out.width="300px"}
print.palette = function(x, ...){
  n = length(x)
  old = par(mar = c(0.5,0.5,0.5,0.5))
  on.exit(par(old))
  image(1:n, 1, as.matrix(1:n), col = x,
        ylab = "", xaxt = "n", yaxt = "n", bty = "n")

  rect(0, 0.9, n + 1, 1.1, col = rgb(1, 1, 1, 0.8), border = NA)
  text((n + 1) / 2, 1, labels = attr(x, "name"), cex = 1, family = "Lato", col = "#32373D")
}

for(name in names(bojack_palettes)){
  (print.palette(bojack_palette(name)))
}
```

